---
title: "Retrieving trophic information from SLIME: a how-to."
author: "<Author 1> and <Author 2>"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SLIMER}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# Load required libraries and functions
library(SLIMER)
```

# Introduction

This vignette demonstrates the use of the functions provided by the SLIMER package for executing SPARQL queries and retrieving trophic information from the SLIME knowledge graph.

# Prerequisites

Before using the functions, make sure to install the SLIMER package and load it:

```{r}
# Install and load the package
# install.packages("./path/to/SLIMER_1.0.0.tar.gz", repos = NULL, type="source")
library(SLIMER)
```

# SPARQL Endpoint Configuration

Set up the SPARQL endpoint URL that you will be querying:

```{r}
# Replace 'endpoint_url' with the actual SPARQL endpoint URL
endpoint_url <- "http://129.88.204.79:7200/repositories/gratin-20240723"
```

# List the datasets integrated in SLIME

Use the get.sources function to retrieve a list of integrated datasets:

```{r}
# Retrieve a list of data sources
sources <- get.sources(endpoint = endpoint_url)

# Display the data frame
print(sources)
```

# Retrieve Metadata for a Specific Data Source

Select a dataset from the obtained list and retrieve its metadata using the get.source.metadata function:

```{r}
# Select a data source
selected_source <- sources[1]

# Retrieve metadata for the selected data source
metadata <- get.source.metadata(source = selected_source, endpoint = endpoint_url)

# Display the metadata
print(metadata)
```

# Retrieve Diets Information

Use the get.diets function to retrieve information about diets based on Taxonomy ID or scientific name:

```{r}
# Example for retrieving diets information based on Taxonomy ID
diets_info <- get.diets(taxid = c("GBIF:2130185", "NCBI:55786"), endpoint = endpoint_url)

print(diets_info)
```

```{r}
# Example for retrieving diets information based on scientific name
diets_info <- get.diets(sciName = c("Tetranychus urticae", "Acrobeles"), endpoint = endpoint_url)

print(diets_info)
```

# Retrieve Interactions Information

Use the get.interactions function to retrieve information about interactions based on Taxonomy ID or scientific name:

```{r}
# Example for retrieving interactions information based on Taxonomy ID
interactions_info <- get.interactions(taxid = c("GBIF:2130185", "NCBI:55786"), endpoint = endpoint_url)

# Display the data frame
print(interactions_info)
```

```{r}
# Example for retrieving interactions information based on scientific name
interactions_info <- get.interactions(sciName = c("Tetranychus urticae", "Acrobeles"), endpoint = endpoint_url)

# Display the data frame
print(interactions_info)
```

# Retrieve Potential Interactions Information

Use the get.potential.interactions function to retrieve information about potential interactions based on Taxonomy ID or scientific name:

```{r}
# Example for retrieving interactions information based on Taxonomy ID
interactions_info <- get.potential.interactions(taxid = c("GBIF:2130185", "NCBI:55786"), endpoint = endpoint_url)

# Display the data frame
print(interactions_info)
```

```{r}
# Example for retrieving potential interactions information based on scientific name
interactions_info <- get.potential.interactions(sciName = c("Tetranychus urticae", "Acrobeles"), endpoint = endpoint_url)

# Display the data frame
print(interactions_info)
```

# Retrieve Guilds Information

Use the get.guilds function to retrieve information about guilds based on Taxonomy ID or scientific name:

```{r}
# Example for retrieving guilds information based on Taxonomy ID
guilds_info <- get.guilds(taxid = c("GBIF:2130185", "NCBI:55786"), endpoint = endpoint_url)

# Display the data frame
print(guilds_info)
```

```{r}
# Example for retrieving guilds information based on scientific name
guilds_info <- get.guilds(sciName = c("Tetranychus urticae", "Acrobeles"), endpoint = endpoint_url)

# Display the data frame
print(guilds_info)
```

# Retrieve Trophic Groups Information

Use the get.trophic.groups function to retrieve information about trophic groups based on Taxonomy ID or scientific name:

```{r}
# Example for retrieving trophic groups information based on Taxonomy ID
groups_info <- get.trophic.groups(taxid = c("GBIF:2130185", "NCBI:55786"), endpoint = endpoint_url)

# Display the data frame
print(groups_info)
```

```{r}
# Example for retrieving trophic groups information based on scientific name
groups_info <- get.trophic.groups(sciName = c("Tetranychus urticae", "Acrobeles"), endpoint = endpoint_url)

# Display the data frame
print(groups_info)
```